INGRID: Creating Languages in MPS from ANTLR Grammars

### 2017-06-09 chapters/background.tex
notes about spoofax

>>>>

\todo{
Mention other state-of-the-art language workbenches: Spoofax.
	Reference: L.C.L. Kats and E. Visser. The Spoofax Language Workbench: Rules for Declarative Specification of Languages and IDEs. OOPSLA 2010
	Eclipse-based IDE support for SDF-based languages.
	Parser-based language workbench.
		Syntax essentially restricted to linear text.
		But it supports language extension and composition.
}
